---
title: "NBA tattoos matter?"
author: "Me"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
# install.packages("fivethirtyeight") # delete this line after installed!!
library(fivethirtyeight)
library(tidyverse)
```

Reading some NBA player stats

```{r}
# Loading nba_tattoos data
#     (from fivethirtyeight pkg)
data("nba_tattoos")

# Loading nba season stats
#     (from https://www.kaggle.com/datasets/justinas/nba-players-data)
nba_season_stats_url <- "https://docs.google.com/spreadsheets/d/1ejAeViZ9Oz4ZgBKi65wdeSTzrdA3aHgDEhHmFGWuozM/export?format=csv"

nba_season_stats <- read.csv(nba_season_stats_url)
```

Do a couple "get to know you" type things with `nba_tattoos` and `nba_season_stats`:

```{r}

nba_season_stats |> 
  group_by(season) |> 
  summarise(n()) |> 
  arrange(season)

```

How do I restrict analysis to just the 2021-22 season?

```{r}

nba_season_stats_21 <- nba_season_stats |> 
  filter(season == "2021-22")


```

How to properly combine the 2 data sources?

```{r}

nba_stattoos <- nba_season_stats_21 |> 
  inner_join(nba_tattoos,
             by = "player_name")

nba_stattoos |> 
  head()
```

How many rows didn't match up to our tattoo data?

```{r}

```

Remove rows with no tattoo data:

```{r}

```

Is the average height of tattoo'd players taller than the inkless?

```{r}

```

Which tattooed player had the highest pts per game?

```{r}

```

Which non-tattooed player had the highest pts per game?

```{r}

```
